A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-13 analysis/paper/paper.Rmd
edit captions in the rmd and the ergm table

```{r table-ergm-terms}
ergm_terms <- readxl::read_excel(here::here("analysis", "data", "raw_data", "ergm_term.xlsx")) 
knitr::kable(ergm_terms,
             caption = "The parameters of exponential random graph models for a undirected network to corresponding with archaeological evidence.")
```

@@

```{r table-posterior-stats}
# make summary table
posterior_esti_two_phases<-
  bergm_two_phases %>%
  pivot_longer(!phase, names_to = "parameter", values_to = "posterior") %>%
  mutate(parameter = factor(parameter,
                            levels=c("edges", "nodematch.age", 
                                     "nodematch.sex", "nodematch.ritual",
                                     "nodematch.value", "gwesp",	
                                     "gwdeg", "dyadcov.distance"))) %>% 
  group_by(parameter, phase) %>% 
  summarize(mean = round(mean(posterior), 2),
            median = round(quantile(posterior, 0.5), 2),
            `2.5%` = round(quantile(posterior, 0.025), 2),
            `97.5%` = round(quantile(posterior, 0.075), 2))

knitr::kable(posterior_esti_two_phases,
             caption = "Estimated posterior means, standard deviation, medians, and 95% credible intervals for the pre-Euroepan model ")
```

@@

```{r figure-bootstrap-CI, fig.cap = "The 95% bootstrap confidence intervals for the observed networks, indicated by 0 nodes removal, and networks with different number of node removal. The number of bootstrap samples is 1000."}
knitr::include_graphics(here::here("analysis", "figures", "007-bootstrap-CI.png"))
```

@@

```{r figure-distribution-moments, fig.cap = "Distribution moments (mean, skewness, variance) calculated on the observed data and simulated distributions for pre- and post- European models."}
knitr::include_graphics(here::here("analysis", "figures", "006-distribution-moments.png"))
```

>>>>

```{r table-ergm-terms}
ergm_terms <- readxl::read_excel(here::here("analysis", "data", "raw_data", "ergm_term.xlsx")) 
knitr::kable(ergm_terms,
             caption = "Network variables used for model specifications with assocaited interpeation for burial relations.")
```

@@

```{r table-posterior-stats}
# tidy data for the table of posterior stats 
posterior_esti_two_phases<-
  bergm_two_phases %>%
  pivot_longer(!phase, 
               names_to = "parameter", 
               values_to = "posterior") %>%
  mutate(parameter = factor(parameter,
                            levels=c("edges", "nodematch.age", 
                                     "nodematch.sex", "nodematch.ritual",
                                     "nodematch.value", "gwesp",	
                                     "gwdeg", "dyadcov.distance"))) %>% 
  group_by(parameter, phase) %>% 
  summarize(mean = round(mean(posterior), 2),
            median = round(quantile(posterior, 0.5), 2),
            `2.5%` = round(quantile(posterior, 0.025), 2),
            `97.5%` = round(quantile(posterior, 0.075), 2)) %>% 
  pivot_wider(names_from = phase, 
              values_from = c(mean, median, `2.5%`, `97.5%`)) %>% 
  select(parameter, ends_with(c("pre", "post")))

library(flextable)
# add column labels
ft <- flextable(posterior_esti_two_phases) %>% 
  set_header_labels(mean_pre = "pre-Euorpean", median_pre = "pre-Euorpean", 
                    `2.5%_pre` = "pre-Euorpean", `97.5%_pre` = "pre-Euorpean",
                    mean_post = "post-Euorpean", median_post = "post-Euorpean", 
                    `2.5%_post` = "post-Euorpean", `97.5%_post` = "post-Euorpean") %>%
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1, j = 6:9, part = "header") %>% 
  add_header_row(values = c("", "mean", "median", "2.5%", "97.5%",
                            "mean", "median", "2.5%", "97.5%"), top = FALSE ) %>% 
  set_caption("Estimated posterior means, medians, and 95% credible intervals for each network parameter of two models.") 
ft
```

@@

```{r figure-bootstrap-CI, fig.cap = "The 95% bootstrap confidence intervals for the observed networks, the top one with 0 nodes removal, and networks with different number of node removal. The number of bootstrap samples is 1000."}
knitr::include_graphics(here::here("analysis", "figures", "007-bootstrap-CI.png"))
```

@@

```{r figure-distribution-moments, fig.cap = "Distribution moments (mean, skewness, and variance) calculated on the observed data and simulated distributions for the pre- and post- European models."}
knitr::include_graphics(here::here("analysis", "figures", "006-distribution-moments.png"))
```
